Evaluation

### 2018-02-15 evaluation.Rmd

# Setup rodent observations
species_abundance = portalr::abundance(shape='flat', level='Site') %>%
  rename(actual = abundance) %>%
  mutate(level='All',currency='abundance') %>%
  left_join(new_moons, by='period') %>%
  filter(species %in% species_of_interest)

total_abundance = portalr::abundance(shape='flat', level='Site') %>%
  group_by(period) %>%
  summarise(actual=sum(abundance)) %>%
  ungroup() %>%
  mutate(level='All',currency='abundance',species='total') %>%
  left_join(new_moons, by='period')

@@

This graph shows the forecast error of some recent forecasts for the most recent sampling dates. This is shown for all model types in the columns and several common rodent species (and total rodents) in the rows. These forecasts are for the entire site. 
```{r recent_eval, echo=FALSE, message=TRUE, warning=FALSE,, fig.width=15, fig.height=15}
###############################################
#Get all the recent forecasts
forecast_data = compile_forecasts(use_hindcasts = FALSE) %>%
  filter(model %in% models_of_interest)

@@

These graphs show errors as a function of lead time. The lead time is the number of months into the future that forecast is made. The error values are an average of all forecast errors using observations since 2010. Note that this currently uses hindcasts of the prior observations.

>>>>

# Setup rodent observations
species_abundance = portalr::abundance(shape='flat', level='Controls') %>%
  rename(actual = abundance) %>%
  mutate(level='Controls',currency='abundance') %>%
  left_join(new_moons, by='period') %>%
  filter(species %in% species_of_interest)

total_abundance = portalr::abundance(shape='flat', level='Controls') %>%
  group_by(period) %>%
  summarise(actual=sum(abundance)) %>%
  ungroup() %>%
  mutate(level='Controls',currency='abundance',species='total') %>%
  left_join(new_moons, by='period')

@@

This graph shows the forecast error of some recent forecasts for the most recent sampling dates. This is shown for all model types in the columns and several common rodent species (and total rodents) in the rows. These evaluations are for the Control plots where no manipulation is done. 
```{r recent_eval, echo=FALSE, message=TRUE, warning=FALSE,, fig.width=15, fig.height=15}
###############################################
#Get all the recent forecasts
forecast_data = compile_forecasts(use_hindcasts = FALSE) %>%
  filter(model %in% models_of_interest)

@@

These graphs show errors as a function of lead time. The lead time is the number of months into the future that forecast is made. The error values are an average of all forecast errors using observations since 2010. Note that this currently uses hindcasts of the prior observations, and is also only for the Control plots.
